---
title: "MY PROJECT"
date: "01-11-2016"
output:
  html_document:
    theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->

<!-- Enter the code required to load your data in the space below. The data will be loaded but the line of code won't show up in your write up (echo=FALSE) in order to save space-->
```{r echo=FALSE}
source("http://www.openintro.org/stat/data/present.R")
```

<!-- In the remainder of the document, add R code chunks as needed -->

### Introduction:

Insert introduction here...

### Data:

Dimension of the Data:

```{r}
dim(present)
```

Name of column:
```{r}
names(present)
```


### Exploratory data analysis:

Insert exploratory data analysis here...
get the count of girls each year
```{r}
present$girls
```

Trent of girls born over years
```{r}
plot(x= present$year, y=present$girls, type = "l")
```

Max of number of birth
```{r}
tempColumn=present$boys+present$girls
present[which(tempColumn==max(tempColumn)),]$year
```

Plot of ratio of boys' born over time
```{r}
plot(present$year, present$boys/(present$boys+present$girls), type = "l")
```

Comparison of boy over girls over time

```{r}
present$boys > present$girls
```

Boy to girl ratio
```{r}
plot(present$year, present$boys/(present$girls), type = "l")
```

Biggest absolute difference 
```{r}
tempColumn=abs(present$boys-present$girls)
present[which(tempColumn==max(tempColumn)),]$year
```


### Inference:

Insert inference section here...

### Conclusion:

Insert conclusion here...

### References:

Insert references here...

### Appendix:

Insert appendix here...