---
title: "titanic_data_explore"
output: html_document
---

Uploading the data

```{r}
train=read.csv("train.csv")
test=read.csv("test.csv")
unsurvived=subset(train, train$Survived==0)
survived=subset(train, train$Survived==1)

```

Data Exploration
Bar Plot for Passenger Survived by Sex
```{r, echo=FALSE}
train_survived_gender_count<-table(subset(train, train$Survived==1)$Sex)
barplot(train_survived_gender_count)

```

Histogram for Passenger by Age

```{r}
hist(survived$Age)
hist(unsurvived$Age)
```

Mean and Standard deviation of Survived
```{r}
mean(subset(survived,survived$Age!='NA')$Age)
sd(subset(survived,survived$Age!='NA')$Age)
```

Mean and Standard deviation of unsurvived

```{r}
mean(subset(unsurvived,unsurvived$Age!='NA')$Age)
sd(subset(unsurvived,unsurvived$Age!='NA')$Age)
```

Survived and Fare more that 26 and less than 10 histogram

```{r}
survived_fare_more26=subset(survived,survived$Fare>26)
hist(survived_fare_more26$Age, breaks = 30)
mean(survived_fare_more26$Age, na.rm = T)
sd(survived_fare_more26$Age, na.rm = T)

survived_fare_less26=subset(survived,survived$Fare<=26)
hist(survived_fare_less26$Age, breaks = 30)
mean(survived_fare_less26$Age, na.rm = T)
sd(survived_fare_less26$Age, na.rm = T)

unsurvived_fare_more10=subset(unsurvived,unsurvived$Fare>10.5)
hist(unsurvived_fare_more10$Age, breaks = 30)
mean(unsurvived_fare_more10$Age, na.rm = T)
sd(unsurvived_fare_more10$Age, na.rm = T)

unsurvived_fare_less10=subset(unsurvived,unsurvived$Fare<=10.5)
hist(unsurvived_fare_less10$Age, breaks = 30)
mean(unsurvived_fare_less10$Age, na.rm = T)
sd(unsurvived_fare_less10$Age, na.rm = T)


```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
