Data 

```{r}
mydata <- read.csv("http://www.ats.ucla.edu/stat/data/binary.csv")
head(mydata)
summary(mydata)
```

Getting Standard Deviation from the data

```{r}
sapply(mydata, sd)
```

```{r}
## two-way contingency table of categorical outcome and predictors
## we want to make sure there are not 0 cells
xtabs(~ admit + rank, data = mydata)
```


Using Logit Model

```{r}
mydata$rank<-factor(mydata$rank)
mylogit=glm(admit ~ gre+gpa+rank, data = mydata, family = "binomial")
summary(mylogit)
```

Co-efficient CIs

```{r}
## CIs using profiled log-likelihood
confint(mylogit)
## CIs using standard errors
confint.default(mylogit)
```

Chi-Square Test

```{r}
wald.test(b = coef(mylogit), Sigma = vcov(mylogit), Terms = 4:6)
```

chi-square test on rank 2 and rank 3

```{r}
l <- cbind(0,0,0,1,-1,0)
wald.test(b = coef(mylogit), Sigma = vcov(mylogit), L = l)
```


From probability to odds to log of odds

Everything starts with the concept of probability.  Let's say that the probability of success of some event is .8.  Then the probability of failure is 1- .8 = .2.  The odds of success are defined as the ratio of the probability of success over the probability of failure.  In our example, the odds of success are .8/.2 = 4.  That is to say that the odds of success are  4 to 1.  If the probability of success is .5, i.e., 50-50 percent chance, then the odds of success is 1 to 1. 


```{r}
## odds ratios only
exp(coef(mylogit))
## odds ratios and 95% CI
exp(cbind(OR = coef(mylogit), confint(mylogit)))
```


We will start by calculating the predicted probability of admission at each value of rank, holding gre and gpa at their means. First we create and view the data frame.

```{r}
newdata1 <- with(mydata,
  data.frame(gre = mean(gre), gpa = mean(gpa), rank = factor(1:4)))

## view data frame
newdata1
```

Prediction

```{r}
newdata1$rankP =predict(mylogit, newdata = newdata1, type = "response")
newdata1
```

