---
title: "MY PROJECT"
date: "01-11-2016"
output:
  html_document:
    theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->

<!-- Enter the code required to load your data in the space below. The data will be loaded but the line of code won't show up in your write up (echo=FALSE) in order to save space-->
```{r echo=FALSE}
load(url("http://www.openintro.org/stat/data/ames.RData"))
population <- ames$Gr.Liv.Area
samp <- sample(population, 60)
```

My distribution should be similar to others' distributions who also collect random samples from this population, but it is likely not exactly the same since it's a random sample. 

A) True 
B) False 

answer: a

```{r}
sample_mean <- mean(samp)
se <- sd(samp)/sqrt(60)
lower <- sample_mean - 1.96 * se
upper <- sample_mean + 1.96 * se

```


For the confidence interval to be valid, the sample mean must be normally distributed and have standard error s/n???s/n. Which of the following is not a condition needed for this to be true? 

A) The sample is random. 
B) The sample size, 60, is less than 10% of all houses. 
C) The sample distribution must be nearly normal. 

answer: c

What does "95% confidence" mean? 

A) 95% of the time the true average area of houses in Ames, Iowa, will be in this interval. 
B) 95% of random samples of size 60 will yield confidence intervals that contain the true average area of houses in Ames, Iowa. 
95% of the houses in Ames have an area in this interval. 
C) 95% confident that the sample mean is in this interval. 

answer: a

What proportion of 95% confidence intervals would you expect to capture the true population mean? 

A) 1% 
B) 5% 
c) 95% 
D) 99% 

answer: d

```{r}
samp_mean <- rep(NA, 50)
samp_sd <- rep(NA, 50)
n <- 60

for(i in 1:50){
  samp <- sample(population, n) # obtain a sample of size n = 60 from the population
  samp_mean[i] <- mean(samp)    # save sample mean in ith element of samp_mean
  samp_sd[i] <- sd(samp)        # save sample sd in ith element of samp_sd
}

lower <- samp_mean - 1.96 * samp_sd / sqrt(n) 
upper <- samp_mean + 1.96 * samp_sd / sqrt(n)
c(lower[1],upper[1])
plot_ci(lower, upper, mean(population))

```

What is the appropriate critical value for a 99% confidence level? 

A) 0.01 
B) 0.99 
C) 1.96 
D) 2.33 
E) 2.58 
```{r}
qnorm(.995)

```
answer: e

We would expect 99% of the intervals to contain the true population mean. 

A) True 
B) False 

answer: true
