


### Data:
load data
```{r}
load(url("http://www.openintro.org/stat/data/mlb11.RData"))
```

What type of plot would you use to display the relationship between runs and one of the other numerical variables? 

A) histogram 
B) box plot 
C) scatterplot 
D) bar plot

answer: c

Plot the relationship between runs and at_bats, using at_bats as the explanatory variable. 
The relationship appears to be . 

A) linear 
B) negative 
C) horseshoe-shaped (??????) 
D) u-shaped (??????)

answer: a

```{r}
plot(mlb11$at_bats,mlb11$runs,main = "Scatterplot Example", xlab = "At Bats", ylab = "Runs")
```
co-relation between runs and at_bats

```{r}
cor(mlb11$runs,mlb11$at_bats)
```

Looking at your plot from the previous exercise, which of the following best describe the relationship between these two variables? 

A) The relationship is negative, linear, and moderately strong. One of the potential outliers is a team with approximately 5520 at bats. 
B) The relationship is positive, linear, and moderately strong. One of the potential outliers is a team with approximately 5520 at bats. 
C) The relationship is positive, linear, and very weak. There are no outliers. 
D) The relationship is positive, linear, and very weak. One of the potential outliers is a team with approximately 5520 at bats.

answer: b

Linear Regression Model over at_bats & runs: 
```{r}
m1 <- lm(runs ~ at_bats, data = mlb11)
summary(m1)
```

Linear Regression Model over homeruns & runs: 
```{r}
m2<-lm(runs~homeruns, data = mlb11)
summary(m2)
```


Fit a new model that uses homeruns to predict runs. Using the estimates from the R output, write the equation of the regression line. What does the slope tell us in the context of the relationship between success of a team and its home runs? 

A) For each additional home run, the model predicts 1.83 more runs, on average. 
B) Each additional home run increases runs by 1.83. 
C) For each additional home run, the model predicts 1.83 fewer runs, on average. 
D) For each additional home run, the model predicts 415.24 more runs, on average. 
E) For each additional home run, the model predicts 415.24 fewer runs, on average.

answer: a

Let's create a scatterplot with the least squares line laid on top.

```{r}
plot(mlb11$runs ~ mlb11$at_bats)
abline(m1)
```

To find the observed number of runs for the team with 5,579 at bats we can use the following:
```{r}
observed_at_bats_5579=mlb11$runs[mlb11$at_bats == 5579]
observed_at_bats_5579

#predicted value from linear regression
predicted_at_bats_5579=m1$fitted.values[mlb11$at_bats == 5579]
predicted_at_bats_5579

#residual
observed_at_bats_5579 - predicted_at_bats_5579
#residual from model
m1$residuals[which(mlb11$at_bats==5579)]
```

What is the residual for the prediction of runs for a team with 5,579 at-bats? Choose the closest answer. 

A) -15.32 
B) 15.32 
C) 713 
D) 5,579

answer: A

Model diagnostics
To assess whether the linear model is reliable, we need to check for (1) linearity, (2) nearly normal residuals, and (3) constant variability.

(1) Linearity: You already checked if the relationship between runs and at-bats is linear using a scatterplot. We should also verify this condition with a plot of the residuals vs. at-bats. Recall that any code following a # is intended to be a comment that helps understand the code but is ignored by R.

```{r}
plot(m1$residuals ~ mlb11$at_bats)
abline(h = 0, lty = 3)
```

Which of the following statements about the residual plot is false? 

A) The residuals appear to be randomly distributed around 0. 
B) The residuals show a curved pattern. 
C) The plot is indicative of a linear relationship between runs and at-bats. 
D) The team with a very high residual compared to the others appears to be an outlier.

answer: b

(2) Nearly normal residuals: To check this condition, we can look at a histogram

```{r}
hist(m1$residuals)
qqnorm(m1$residuals)
qqline(m1$residuals)
```

Which of the following is true? 

A)The residuals are extremely right skewed, hence the normal distribution of residuals condition is not met. 
B) The residuals are extremely left skewed, hence the normal distribution of residuals condition is not met. 
C) The residuals are perfectly symmetric, hence the normal distribution of residuals condition is met. 
D) The residuals are fairly symmetric, with only a slightly longer tail on the right, hence it would be appropriate to deem the the normal distribution of residuals condition met.

answer: d

Based on the plot in (1), the constant variability condition appears to be met. 

A) True 
B) False

answer: a

```{r}
m3<-lm(runs~at_bats, data = mlb11)
summary(m3)
m4<-lm(runs~hits, data = mlb11)
summary(m4)
m5<-lm(runs~wins, data = mlb11)
summary(m5)
m6<-lm(runs~bat_avg, data = mlb11)
summary(m6)
```

Now that you can summarize the linear relationship between two variables, investigate the relationships between runs and each of the other five traditional variables. Which variable best predicts runs? 

A) at bats 
B) hits 
C) wins 
D) batting average

answer: d

Now examine the three newer variables. These are the statistics used by the author of Moneyball to predict a teams success. In general, are they more or less effective at predicting runs that the old variables? Explain using appropriate graphical and numerical evidence. Of all ten variables we've analyzed, which seems to be the best predictor of runs? 
A) on-base plus slugging (new_obs) 
B) slugging percentage (new_slug) 
C) on-base percentage (new_onbase)

answer: a

```{r}
m7<-lm(runs~new_obs, data = mlb11)
summary(m7)
plot(m7$residuals ~ mlb11$new_obs)
abline(h = 0, lty = 3)

m8<-lm(runs~new_slug, data = mlb11)
summary(m8)
plot(m8$residuals ~ mlb11$new_slug)
abline(h = 0, lty =3)

m9<-lm(runs~new_onbase, data = mlb11)
summary(m9)
plot(m9$residuals ~ mlb11$new_onbase)
abline(h = 0, lty=3)
```

